
# MdFOCuS simulations

To run the 3-dimensional simulations, run in order the scripts:
- 1-p3_avg_run_length.R
- 2-p3_detection_delay.R

To run the 5-dimensional simulations, run in order the scripts:
- 3-p5_avg_run_length.R
- 4-p5_detection_delay.R

Once those have run, the code below generates the tables presented in the paper:

## 3 dimentional sequences.

```{r, include=FALSE}
source("helper_functions.R")
p <- 3
N <- 5000
file <- paste0("det_del_", "p", p, "N", N, ".RData")

load(file)
tot_res <- Reduce(rbind, runs_res)

tot_summ <- tot_res %>% mutate(dd = est - 500, density = density * p) %>% 
  group_by(magnitude, density, algo) %>%
  summarise(avg_dd = mean(if_else(dd < 0, NA, dd), na.rm = T), sd_dd = sd(if_else(dd < 0, NA, dd), na.rm = T), fpr = mean(dd<0))
```


### Pre-change mean known

Generates the latex tables:

```{r echo=FALSE}
tot_summ %>% 
  filter(algo %in% c("FOCuS0", "md-FOCuS0", "ocd (ora)"), magnitude < 2) %>%
  pivot_wider(names_from = algo, values_from = avg_dd, id_cols = -c(fpr, sd_dd)) %>% xtable::xtable(digits = 2) %>% print(include.rownames = F)
tot_summ %>% filter(algo %in% c("FOCuS0", "md-FOCuS0", "ocd (ora)"), magnitude < 2) %>% group_by(magnitude, algo) %>%
  summarise(sd_dd = sd(sd_dd)) %>%
  pivot_wider(names_from = algo, values_from = sd_dd)  %>% xtable::xtable() %>% xtable::xtable() %>% print(include.rownames = F)
```

### Pre-change mean unknown

```{r echo=FALSE}
tot_summ %>%
  filter(algo %in% c("FOCuS", "md-FOCuS", "ocd (est)", "FOCuS0 (est)"), magnitude > 0.25) %>%
  pivot_wider(names_from = algo, values_from = avg_dd, id_cols = -c(fpr, sd_dd)) %>% xtable::xtable() %>% print(include.rownames = F)
tot_summ %>% filter(algo %in% c("FOCuS", "md-FOCuS", "ocd (est)", "FOCuS0 (est)"), magnitude > 0.25) %>% group_by(magnitude, algo) %>%
  summarise(sd_dd = sd(sd_dd)) %>%
  pivot_wider(names_from = algo, values_from = sd_dd) %>% xtable::xtable() %>% print(include.rownames = F)
```

## 5 dimentional sequences.
```{r, include=FALSE}
source("helper_functions.R")
p <- 5
N <- 5000
file <- paste0("det_del_", "p", p, "N", N, ".RData")

load(file)
tot_res <- Reduce(rbind, runs_res)

tot_summ <- tot_res %>% mutate(dd = est - 500, density = density * p) %>% 
  group_by(magnitude, density, algo) %>%
  summarise(avg_dd = mean(if_else(dd < 0, NA, dd), na.rm = T), sd_dd = sd(if_else(dd < 0, NA, dd), na.rm = T), fpr = mean(dd<0))
```

### Pre-change mean known
```{r echo=FALSE}
tot_summ %>% 
  filter(algo %in% c("FOCuS0", "md-FOCuS0", "ocd (ora)"), magnitude < 2) %>%
  pivot_wider(names_from = algo, values_from = avg_dd, id_cols = -c(fpr, sd_dd)) %>% xtable::xtable() %>% xtable::xtable() %>% print(include.rownames = F)
tot_summ %>% filter(algo %in% c("FOCuS0", "md-FOCuS0", "ocd (ora)"), magnitude < 2) %>% group_by(magnitude, algo) %>%
  summarise(sd_dd = sd(sd_dd)) %>%
  pivot_wider(names_from = algo, values_from = sd_dd) %>% xtable::xtable() %>% xtable::xtable() %>% print(include.rownames = F)
```
### Pre-change mean unknown
```{r echo=FALSE}
tot_summ %>%
  filter(algo %in% c("FOCuS", "md-FOCuS", "ocd (est)", "FOCuS0 (est)"), magnitude > 0.25) %>%
  pivot_wider(names_from = algo, values_from = avg_dd, id_cols = -c(fpr, sd_dd)) %>% xtable::xtable() %>% xtable::xtable() %>% print(include.rownames = F)
tot_summ %>% filter(algo %in% c("FOCuS", "md-FOCuS", "ocd (est)", "FOCuS0 (est)"), magnitude > 0.25) %>% group_by(magnitude, algo) %>%
  summarise(sd_dd = sd(sd_dd)) %>%
  pivot_wider(names_from = algo, values_from = sd_dd) %>% xtable::xtable() %>% xtable::xtable() %>% print(include.rownames = F)
```